An Online Visual Loop Closure Detection Method for Indoor Robotic Navigation

### 2014-11-30 latex-spie/article.tex
Benchmark dataset keywords are added

The method implemented in this paper has been evaluated on three datasets which lighting is different from one another.

@@

@@

\subsection{Experimental Setup}

>>>>

The method implemented in this paper has been evaluated on three datasets which lighting conditions are different from one another.

@@

manually annotated
Moving platform,
indoor
Kinect (grayscale and depth images) 
Kinect: max line of sight is 10m
Average speed is approx 0.5 m/s 
bright, dim, dark (to evaluate depth info)
bright 2082, dim 2083, dark 2251
approx 1000 frames per loop
2 loops, each dataset approx 2000 frames
1 loop for loop closure testing
examples shown in \ref{fig:dataset}

@@
